---
title: "Argo Track Animations"
author: "Jessica Kendall-Bar"
format: html
editor: visual
---

# Visualizing Heat in the Deep Ocean with Argo

This website contains detailed instructions for re-creating the visualizations used in the Argo Animation produced in November 2023 for presentation at the Ocean Pavilion for the United Nations Climate Change Conference, COP28, in Dubai November 30-December 12, 2023.

## Heat in the deep: Scientists use Argo to track heat added to our global ocean

**Description:** Extreme weather events and sea level rise are increasing, intensified by a warming ocean. Understanding heat in the ocean can help better predict extreme weather and long-term climate shifts. A network of robotic instruments called Argo is helping scientists track warming beneath the surface and it's showing us the ocean's heat content is increasing steeply.  This video shares just how much the ocean is warming, and how the Argo program needs more support to continue to give society the full picture of ocean warming. 

#Argo #OceanWarming #OceanHeat #MarineHeatWaves #ScrippsOceanography #UCSanDiego 

{{< video https://www.youtube.com/embed/wo9vZccmqwc >}}

#### Animation by Jessica Kendall-Bar. <https://jessiekb.com> 

**Science Advisors:** Sarah Purkey & Megan Scanderbeg - Climate, Atmospheric Sciences, and Physical Oceanography, Scripps Institution of Oceanography, UC San Diego.

Want to understand these changes better? Increased sea surface temperature is contributing to large-scale warming of our oceans. When this temperature change is distributed over the large ocean volume, it contains a lot of heat energy. Since the 1980s, the ocean has accumulated over 176 zetta-Joules of heat energy, roughly the equivalent of 7 billion atomic bombs. \
\
While the warming is clear, there are also some smaller, localized instances of apparent cooling, such as in the Drake's passage below South America. In this case, this is due to shifts in ocean circulation including the intensity and location of Southern Ocean zonal flow. Read more about these changes here: <https://www.nature.com/articles/s41558-021-01212-5>

\-\-\--

Argo data are collected and made freely available by the International Argo Program and the national programs that contribute to it. 

**Argo Website: <https://argo.ucsd.edu>**

**Publication: <https://doi.org/10.17882/42182>**

*Other data sources (in order of appearance):*

Sea Surface Temperature (SST) data from the Jet Propulsion Laboratory Multi-scale Ultra-high Resolution (MUR) Sea Surface Temperature Analysis. <https://svs.gsfc.nasa.gov/cgi-bin/details.cgi?aid=5101> 

Monthly Global Sea Surface Temperature Timeseries: OISST V2.1 - ClimateReanalyzer.org, Climate Change Institute, University of Maine. <https://climatereanalyzer.org/clim/sst_monthly/> 

Internal ocean temperature difference: Roemmich-GiIson Argo Climatology (2009). Anomaly calculated from the over Jan 2004 - Dec 2018 average. 

Publication: <http://dx.doi.org/10.1016/j.pocean.2009.03.004> \
Dataset: <https://sio-argo.ucsd.edu/pub/Global_Marine_Argo_Atlas/RG_ArgoClim_Temp.nc>, 

Ocean heat content: Lyman and Johnson (2014) updated for Johnson et al. (BAMS State of the Climate 2023). <https://www.climate.gov/news-features/understanding-climate/climate-change-ocean-heat-content> 

Code to generate Argo data visualizations is available via Github at: <https://github.com/jmkendallbar/Argo-Animation> 

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

{{< video https://www.youtube.com/embed/wo9vZccmqwc >}}
